---
title: "Katie ROC Regression"
author: "jdt"
date: "2023-09-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# load packages
```{r}

library("tidyverse"); theme_set(theme_classic())
library("boot")
library("pROC")
library("mvtnorm")
library("quantreg")
library("betareg")
library("gamlss")
library("ggplot2")
```
# Simulate binormal data

```{r}

# density functions for Y1 and Y0
Norm_dens <- function(Y, c, d, sd_e){
  dnorm(Y, c + d * .5, sd_e) # mean of U(0, 1) r.v. is 0.5
}

# SCENARIO 1: normal distributions with minimal separation
SC1_H <- list(c = 1.5, d = 3, sd = 1.5)
SC1_D <- list(c = 2, d = 4, sd = 1.5)

ggplot(data.frame(x = c(-4, 10)), aes(x)) +
  stat_function(fun = Norm_dens, args = SC1_H) +
  stat_function(fun = Norm_dens, args = SC1_D, color = "red") +
  xlab("Y") + 
  ylab("Density")

# SCENARIO 2: normal distributions with considerable separation
SC2_H <- SC1_H
SC2_D <- list(c = 3, d = 6, sd = 1.5)

ggplot(data.frame(x = c(-4, 10)), aes(x)) +
  stat_function(fun = Norm_dens, args = SC2_H) +
  stat_function(fun = Norm_dens, args = SC2_D, color = "red")

# binormal ROC curves for each scenario

# True covariate-adjusted binormal ROC curve
true_binormal_ROC <- function(t, c1, d1, sd1, c0, d0, sd0, X0){
  a <- (c1 + d1 * X0 - (c0 + d0 * X0)) / sd1
  b <- sd0 / sd1
  pnorm(a + b * qnorm(t))
}

# True covariate-adjusted binormal AUC
true_binormal_AUC <- function(c1, d1, sd1, c0, d0, sd0, X0){
  a <- (c1 + d1 * X0 - (c0 + d0 * X0)) / sd1
  b <- sd0 / sd1
  pnorm(a / sqrt(1 + b^2))
}

SC1_H_v <- unlist(SC1_H)
SC1_D_v <- unlist(SC1_D)
```

# SCENARIO 1: TRUE ROC curve and AUC

```{r}

ggplot(data.frame(t = c(0, 1)), aes(t)) +
  stat_function(fun = true_binormal_ROC, args = list(SC1_D_v[1], SC1_D_v[2],
  SC1_D_v[3], SC1_H_v[1], SC1_H_v[2], SC1_H_v[3], X0 = 0.2)) +
  annotate("text", x = 0.7, y = 0.3, 
           label = paste0("AUC = ", true_binormal_AUC(SC1_D_v[1],
           SC1_D_v[2], SC1_D_v[3],
           SC1_H_v[1], SC1_H_v[2], SC1_H_v[3],
           X0 = 0.2) %>% round(3))) +
  ylab("ROC(t)") +
  coord_fixed(ratio = 1)

SC2_H_v <- unlist(SC2_H)
SC2_D_v <- unlist(SC2_D)
```
# SCENARIO 2: TRUE ROC curve and AUC

```{r}

ggplot(data.frame(t = c(0, 1)), aes(t)) +
  stat_function(fun = true_binormal_ROC, 
  args = list(SC2_D_v[1], SC2_D_v[2], SC2_D_v[3], SC2_H_v[1], 
  SC2_H_v[2], SC2_H_v[3], X0 = 0.2)) +
  annotate("text", x = 0.7, y = 0.3, 
           label = paste0("AUC = ",
           true_binormal_AUC(SC2_D_v[1], SC2_D_v[2], SC2_D_v[3],
           SC2_H_v[1], SC2_H_v[2], SC2_H_v[3],
           X0 = 0.2) %>% round(3))) +
  ylab("ROC(t)") +
  coord_fixed(ratio = 1)
```
# function to generate binormal data

```{r}

gen_Norm_data <- function(c0, d0, sd_e0, n0, c1, d1, sd_e1, n1){
  x <- runif(n1)
  eps0 <- rnorm(n0, 0, sd_e0)
  eps1 <- rnorm(n1, 0, sd_e1)
  y0 <- c0 + d0 * x + eps0
  y1 <- c1 + d1 * x + eps1
  
  data.frame(y = c(y0, y1), dis = as.factor(c(rep(0, n0), rep(1, n1))),
             x = rep(x, 2))
}

n_T <- 50
t <- seq(1/n_T, (n_T - 1)/n_T, 1/n_T) # set of FPRs considered
```

```{r}

set.seed(2433)
# generate 1,000 datasets  # Changed to 100
dats <- replicate(100, gen_Norm_data(1.5, 3, 1.5, 200, 2, 4, 1.5, 200), 
simplify = FALSE)

```

# 2. Functions to calculate ROC for each method
# A. parametric distribution-free method (PDF)

```{r}

PDF_FUN <- function(data, t){
  df0 <- filter(data, dis == 0)
  df1 <- filter(data, dis == 1)
  
  n1 <- nrow(df1)
  # quantile regression to estimate reference survival
  qr0 <- rq(y ~ x, data = df0, tau = t) 
  
  # covariate adjusted survival for diseased observations
  pred1 <- predict.rq(qr0, newdata = df1)
  
  Inv_t <- qnorm(rev(t)) # normal quantiles of FPRs
  nq <- length(t)        # number of quantiles
  
  # reshaping the data
  t_pred1 <- t(pred1)
  col_pred1 <- c(t_pred1)
  col_t <- rep(Inv_t, n1)
  col_y1 <- rep(df1$y, each = nq)
  col_x <- rep(df1$x, each = nq)
  col_uit <- as.numeric(col_y1 >= col_pred1)
  
  probitData <- data.frame("fdbar" = col_pred1, "phiInv" = col_t, 
  "disRes" = col_y1, "covX" = col_x, "uit" = col_uit)
  
  probMod <- glm(uit ~ phiInv + covX, family = binomial(link = "probit"), 
                  data = probitData)
  probMod$coefficients
}
```

# B. Beta method.
# function that transforms PVs, so they're in the open unit interval

```{r}

dep_trans_betareg <- function(y){
  n_obs <- sum(!(is.na(y)))
  (y * (n_obs - 1) + 0.5) / n_obs
}

Beta_FUN <- function(data, t){
  df0 <- filter(data, dis == 0)
  df1 <- filter(data, dis == 1)
  
  Y_D <- pull(df1, y)
  n1 <- nrow(df1)
  
  # quantile regression to estimate reference survival
  qr0 <- rq(y ~ x, data = df0, tau = t) 
  
  # covariate adjusted survival for diseased observations
  pred1 <- predict.rq(qr0, newdata = df1)
  t_pred1 <- t(pred1)
  pred3 <- lapply(seq_len(ncol(t_pred1)), function(i) t_pred1[,i])
  PV_dis <- mapply(function(x, y) mean(x >= y), x = pred3, y = Y_D) 
  datdis <- data.frame(Y_D, x = df1$x, PV_dis)
  
  if(any(datdis$PV_dis == 0 | datdis$PV_dis == 1)){ # transform PVs
    SUM0 <- sum(datdis$PV_dis == 0) # keep PVs = 0
    SUM1 <- sum(datdis$PV_dis == 1) # keep track of PVs = 1
    BetaMod <- betareg(dep_trans_betareg(PV_dis) ~ x, data = datdis,
                       link.phi = "identity", link = "logit")
    
    list(BetaMod$coefficients, SUM0 = SUM0, SUM1 = SUM1)
  }else{
    BetaMod <- betareg(PV_dis ~ x, data = datdis,
                       link.phi = "identity", link = "logit")
    
    list(BetaMod$coefficients)
  }
}
```

# C. Inflated Beta method.

```{r}

InfBeta_FUN <- function(data, t){
  df0 <- filter(data, dis == 0)
  df1 <- filter(data, dis == 1)
  
  Y_D <- pull(df1, y)
  n1 <- nrow(df1)
  
  # quantile regression to estimate reference survival
  qr0 <- rq(y ~ x, data = df0, tau = t) 
  
  # covariate adjusted survival for diseased observations
  pred1 <- predict.rq(qr0, newdata = df1)
  t_pred1 <- t(pred1)
  pred3 <- lapply(seq_len(ncol(t_pred1)), function(i) t_pred1[,i])
  PV_dis <- mapply(function(x, y) mean(x >= y), x = pred3, y = Y_D) 
  disdat <<- data.frame(Y_D, x = df1$x, PV_dis)
  
  if(any(disdat$PV_dis == 0) & any(disdat$PV_dis == 1)){ ## BEINF Beta Inflated
    SUM0 <- sum(disdat$PV_dis == 0)
    SUM1 <- sum(disdat$PV_dis == 1)
    Beta_InfMod <<- gamlss(PV_dis ~ x, data = disdat, family = BEINF)
    list(Beta_InfMod$mu.coefficients,
         Beta_InfMod$sigma.coefficients,
         Beta_InfMod$nu.coefficients,
         Beta_InfMod$tau.coefficients, SUM0 = SUM0, SUM1 = SUM1)
  }else if(any(disdat$PV_dis == 0)){      ## BEINF0 Beta Inflated zero
    SUM0 <- sum(disdat$PV_dis == 0)
    Beta_0Inf <<- gamlss(PV_dis ~ x, data = disdat, family = BEINF0)
    list(Beta_0Inf$mu.coefficients,
         Beta_0Inf$sigma.coefficients,
         Beta_0Inf$nu.coefficients, SUM0 = SUM0, SUM1 = 0)
  }else if(any(disdat$PV_dis == 1)){     ## BEINF1 Beta Inflated one
    SUM1 <- sum(disdat$PV_dis == 1)
    Beta_1Inf <- gamlss(PV_dis ~ x, data = disdat, family = BEINF1)
    list(Beta_1Inf$mu.coefficients,
         Beta_1Inf$sigma.coefficients,
         Beta_1Inf$nu.coefficients, SUM0 = 0, SUM1 = SUM1)
  }else{                                 ## Regular beta regression
    BetaMod <- betareg(PV_dis ~ x, data = disdat,
                       link.phi = "identity", link = "logit")
    list(BetaMod$coefficients, SUM0 = 0, SUM1 = 0)
  }
}
```

# 3. Calculate ROC and compute MSE
# for each of the 1,000(100) data sets generated under Scenario 1, I obtain the regression coefficients using the three different methods.

```{r}

PDF_coefs <- sapply(dats, PDF_FUN, t = t, simplify = FALSE)
Beta_coefs <- sapply(dats, Beta_FUN, t = t, simplify = FALSE)
InfBeta_coefs <- sapply(dats, InfBeta_FUN, t = t, simplify = FALSE)

# histograms of the counts of PVs that are zero from the 1,000 data sets.

# get number of PVS that are 0 and 1 for each data set
getNums <- function(coefs, SUM0, SUM1){
  coefs <- unlist(coefs)
  coefs[c(SUM0, SUM1)]
}

PVs_0and1 <- sapply(Beta_coefs, getNums, "SUM0", "SUM1")
df_PVs <- data.frame(t(PVs_0and1))

# histogram of PVs = 0
ggplot(df_PVs, aes(SUM0)) +
  geom_histogram()

# histogram of PVs = 1
ggplot(df_PVs, aes(SUM1))  +
  geom_histogram(bins = 6)

# Determine the difference between the estimator of the covarariate-specific ROC curve and the true ROC curve, I calculate the MSE (defined in the 2011 paper)

# TRUE ROC(t) values for t = 0, 1/50, ..., 1.
T_vals <- mapply(true_binormal_ROC, t = c(0, t, 1), 
X0 = rep(c(0, t, 1), each = length(t) + 2),
MoreArgs = list(c1 = 2, d1 = 4, sd1 = 1.5, c0 = 1.5, d0 = 3, sd0 = 1.5))
                               
# MSE wrapper function
wrapper <- function(coef_vals, ROC_fun){
  mapply(ROC_fun, t = c(0, t, 1), X_val = rep(c(0, t, 1), each = length(t) + 2),
         MoreArgs = list(coef_vals))
}

# function to get PDF ROC for particular t and X_val
binorm_ROC <- function(coefs, t, X_val){
  coefs <- unlist(coefs)
  ga_1 <- coefs[[1]]
  ga_2 <- coefs[[2]]
  Be <- coefs[[3]]
  pnorm(ga_1 + ga_2 * qnorm(t) + Be * X_val)
}

PDF_vals <- sapply(PDF_coefs, wrapper, ROC_fun = binorm_ROC)

MSE_PDF <- apply(PDF_vals, 2, function(x) sum((x - T_vals)^2)/n_T^2)
summary(MSE_PDF) 

# function to get Beta ROC for particular t and X_val
Beta_ROC <- function(coefs, t, X_val){
  coefs <- unlist(coefs)
  Be_hat0 <- coefs[[1]]
  Be_hat1 <- coefs[[2]]
  phi_hat <- coefs[[3]]
  
  a_hat <- phi_hat/(1 + exp(-Be_hat0 -X_val * Be_hat1))
  b_hat <- phi_hat * (1 - 1/(1 + exp(-Be_hat0 -X_val * Be_hat1)))
  pbeta(t, a_hat, b_hat)
}

Be_vals <- sapply(Beta_coefs, wrapper, ROC_fun = Beta_ROC)

MSE_Be <- apply(Be_vals, 2, function(x) sum((x - T_vals)^2)/n_T^2)
summary(MSE_Be)

# function to get Inf Beta ROC for particular t and X_val
InfBeta_ROC <- function(coefs, t, X_val){
  coefs <- unlist(coefs)
  
  if(coefs["SUM0"] > 0 | coefs["SUM1"] > 0){ ## BEINF/BEINF0/BEINF1
    mu.c1 <- coefs[[1]]
    mu.c2 <- coefs[[2]]
    mu <- 1 / (1 + exp(-mu.c1 - X_val * mu.c2))
    sig.c <- coefs[[3]]
    sig <- 1 / (1 + exp(-sig.c))
    nu.c <- coefs[[4]]
    nu <- exp(nu.c)
    if(coefs["SUM0"] > 0 & coefs["SUM1"] > 0){ ## BEINF cdf
      tau.c <- coefs[[5]]
      tau <- exp(tau.c)
      pBEINF(t, mu, sig, nu, tau)
    }else if(coefs["SUM0"] > 0){               ## BEINF0 cdf
      pBEINF0(t, mu, sig, nu)
    }else if(coefs["SUM1"] > 0){               ## BEINF1 cdf
      pBEINF1(t, mu, sig, nu)
    } 
  }else{                                       ## Beta cdf
    Be_hat0 <- coefs[[1]]
    Be_hat1 <- coefs[[2]]
    phi_hat <- coefs[[3]]
    
    a_hat <- phi_hat/(1 + exp(-Be_hat0 -X_val * Be_hat1))
    b_hat <- phi_hat * (1 - 1/(1 + exp(-Be_hat0 -X_val * Be_hat1)))
    pbeta(t, a_hat, b_hat)
  }
}

outputInf <- sapply(InfBeta_coefs, wrapper, ROC_fun = InfBeta_ROC)
MSE_Inf <- apply(outputInf, 2, function(x) sum((x - T_vals)^2)/n_T^2)
summary(MSE_Inf)

```

# Boxplots of the MSE values for each method

```{r}
datMSE <- data.frame(MSE = c(MSE_PDF, MSE_Be, MSE_Inf), 
type = c(rep("PDF", length(MSE_PDF)), rep("Beta", length(MSE_Be)),
rep("InfBeta", length(MSE_Inf))))

ggplot(datMSE, aes(type, MSE)) +
  geom_boxplot()

## Repeat process of finding the ROCs and MSEs for 1,000 data sets except this time under Scenario 2, where the two populations are considerably separated.

# generate 1,000 data sets  # chnaged to 100
dats2 <- replicate(100, gen_Norm_data(1.5, 3, 1.5, 200, 3, 6, 1.5, 200), 
simplify = FALSE)

# ROC regression coefficients for multiple datasets
PDF_coefs2 <- sapply(dats2, PDF_FUN, t = t, simplify = FALSE)
Beta_coefs2 <- sapply(dats2, Beta_FUN, t = t, simplify = FALSE)
InfBeta_coefs2 <- sapply(dats2, InfBeta_FUN, t = t)

PVs_0and1_2 <- sapply(Beta_coefs2, getNums, "SUM0", "SUM1")
df_PVs2 <- data.frame(t(PVs_0and1_2))

# histogram of PVs = 0
ggplot(df_PVs2, aes(SUM0)) +
  geom_histogram()

# histogram of PVs = 1
ggplot(df_PVs2, aes(SUM1))  +
  geom_histogram(bins = 3)

# TRUE ROC(t) values for t = 0, 1/50, ..., 1.
T_vals2 <- mapply(true_binormal_ROC, t = c(0, t, 1), X0 = rep(c(0, t, 1), 
each = length(t) + 2), 
MoreArgs = list(c1 = 3, d1 = 6, sd1 = 1.5, c0 = 1.5, d0 = 3, sd0 = 1.5))

PDF_vals2 <- sapply(PDF_coefs2, wrapper, ROC_fun = binorm_ROC)

MSEs2 <- apply(PDF_vals2, 2, function(x) sum((x - T_vals2)^2)/n_T^2)
summary(MSEs2)

outputBe2 <- sapply(Beta_coefs2, wrapper, ROC_fun = Beta_ROC)

MSE_Bes2 <- apply(outputBe2, 2, function(x) sum((x - T_vals2)^2)/n_T^2)
summary(MSE_Bes2)

outputInf2 <- sapply(InfBeta_coefs2, wrapper, ROC_fun = InfBeta_ROC)
MSE_Inf2 <- apply(outputInf2, 2, function(x) sum((x - T_vals2)^2)/n_T^2)
summary(MSE_Inf2)

# Boxplots of the MSE values for each method

datMSE <- data.frame(MSE = c(MSE_PDF, MSE_Be, MSE_Inf), 
type = c(rep("PDF", length(MSE_PDF)), rep("Beta", length(MSE_Be)),
rep("InfBeta", length(MSE_Inf))))

ggplot(datMSE, aes(type, MSE)) +
  geom_boxplot()
```

#Application using the South African Heaert Disease Data

```{r, warning=FALSE}

# load packages
library("tidyverse"); theme_set(theme_classic())
library("pROC")
library("quantreg")
library("betareg")

# load data
dat <- read.csv("SAHeart_Disease.csv")
dat$row.names <- NULL
dat$famhist <- ifelse(dat$famhist == "Present", 1, 0) %>% factor()

# Empirical AUC of ldl
roc(dat$chd, dat$ldl)

# selecting variables for ROC regression
dat_mod <- dplyr::select(dat, chd, age, ldl, famhist, tobacco)

n_T <- 50
t <- seq(1/n_T, (n_T - 1)/n_T, 1/n_T) # set of FPRs

# 1. PDF ROC on SA chd data set
PDF_fun <- function(data, t){
  df0 <- filter(data, chd == 0)
  df1 <- filter(data, chd == 1)
  
  n1 <- nrow(df1)
  # quantile regression to estimate reference survival
  qr0 <- rq(ldl ~ famhist + age + tobacco, data = df0, tau = t)
  
  # covariate adjusted survival for diseased observations
  pred1 <- predict.rq(qr0, newdata = df1)
  
  Inv_t <- qnorm(rev(t))  # normal quantiles of FPRs
  nq <- length(t)         # number of quantiles
  
  # reshaping the data
  t_pred1 <- t(pred1)
  col_pred1 <- c(t_pred1)
  col_t <- rep(Inv_t, n1)
  col_ldl <- rep(df1$ldl, each = nq)
  col_age <- rep(df1$age, each = nq)
  col_tobacco <- rep(df1$tobacco, each = nq)
  col_famhist <- rep(df1$famhist, each = nq)
  col_uit <- as.numeric(col_ldl >= col_pred1)
  
  probitData <- data.frame(fdbar = col_pred1, phiInv = col_t,
                           ldl = col_ldl, age = col_age,
                           tobacco = col_tobacco, famhist = col_famhist,
                           uit = col_uit)
  probMod <- glm(uit ~ phiInv + famhist + age + tobacco, 
                 family = binomial(link = "probit"), data = probitData)
  summary(probMod)
}

coefs_PDF <- PDF_fun(dat_mod, t = t)$coefficients[,1]   # coefficients
coefs_PDF

# bootstrapping SEs
B <- 100    #changed to 100
results <- matrix(NA ,nrow = B, ncol = 5)
for(b in 1:B){
  boot_dat <- dat_mod[sample(nrow(dat_mod), nrow(dat_mod),
                             replace = TRUE),]
  results[b,] <- PDF_fun(boot_dat, t = t)$coefficients[,2]
}

colMeans(results) # Bootstrap SEs for coefficients

# get z statistics and p-values
get_sigs <- function(estimate, std_error){
  z <- estimate / std_error
  c(z, ifelse(z > 0, pnorm(z, lower.tail = FALSE) * 2,
         pnorm(z) * 2))
}
map2(.x = coefs_PDF,
     .y = colMeans(results), get_sigs)

# Estimate of AUC: age = 45, famhist = 1, tobacco = 5
pnorm((coefs_PDF[1] + coefs_PDF[3] + coefs_PDF[4] * 45 +
         coefs_PDF[5] * 5)/sqrt(1 + coefs_PDF[2]^2))

# 2. Beta ROC on SA chd data set

# function that transforms PVs, so they're in the open unit interval
dep_trans_betareg <- function(y){
  n_obs <- sum(!(is.na(y)))
  (y * (n_obs - 1) + 0.5) / n_obs
}

Beta_FUN <- function(data, t){
  df0 <- filter(data, chd == 0)
  df1 <- filter(data, chd == 1)
  
  Y_ldl <- pull(df1, ldl)
  n1 <- nrow(df1)
  
  # quantile regression to estimate reference survival
  qr0 <<- rq(ldl ~ famhist + age + tobacco, data = df0, tau = t) 
  
  # covariate adjusted survival for diseased observations
  pred1 <<- predict.rq(qr0, newdata = df1)
  t_pred1 <- t(pred1)
  pred3 <- lapply(seq_len(ncol(t_pred1)), function(i) t_pred1[,i])
  PV_dis <<- mapply(function(x, y) mean(x >= y), x = pred3, y = Y_ldl) 
  datdis <<- data.frame(Y_ldl, age = df1$age, 
                        famhist = df1$famhist, tobacco = df1$tobacco,
                        PV_dis)
  
  if(any(datdis$PV_dis == 0 | datdis$PV_dis == 1)){ # transform PVs if any are 0 or 1
    SUM0 <- sum(datdis$PV_dis == 0)
    SUM1 <- sum(datdis$PV_dis == 1)
    BetaMod <<- betareg(dep_trans_betareg(PV_dis) ~ famhist + age + tobacco, 
                       data = datdis,
                       link.phi = "identity", link = "logit")
    
    BetaMod$coefficients
  }else{
    BetaMod <- betareg(PV_dis ~ famhist + age + tobacco, data = datdis,
                       link.phi = "identity", link = "logit")
    
    BetaMod$coefficients
  }
}

coefs_Be <- Beta_FUN(dat_mod, t = t)    # coefficients
coefs_Be

# function to get Beta AUC
Beta_AUC <- function(coefs, X_val = matrix(c(1, 1, 45, 5), nrow = 4)){
  coefs <- unlist(coefs)
  Be_hat0 <- coefs[[1]]
  Be_hat_fh <- coefs[[2]]
  Be_hat_age <- coefs[[3]]
  Be_hat_tob <- coefs[[4]]
  phi_hat <- coefs[[5]]
  
  Be <- matrix(c(Be_hat0, Be_hat_fh, Be_hat_age,
                 Be_hat_tob), ncol = 4)
  
  a_hat <- phi_hat/(1 + exp(-Be %*% X_val))
  b_hat <- phi_hat * (1 - 1/(1 + exp(-Be %*% X_val)))
  # pbeta(t, a_hat, b_hat)    ## ROC
  1 - a_hat / (a_hat + b_hat) ## AUC
}

Beta_AUC(coefs_Be)

# Plotting ROC curves for PDF method and Beta method

Beta_ROC <- function(coefs, t, X_val = matrix(c(1, 1, 45, 5), nrow = 4)){
  coefs <- unlist(coefs)
  Be_hat0 <- coefs[[1]]
  Be_hat_fh <- coefs[[2]]
  Be_hat_age <- coefs[[3]]
  Be_hat_tob <- coefs[[4]]
  phi_hat <- coefs[[5]]
  
  Be <- matrix(c(Be_hat0, Be_hat_fh, Be_hat_age,
                 Be_hat_tob), ncol = 4)
  
  a_hat <- phi_hat/(1 + exp(-Be %*% X_val))
  b_hat <- phi_hat * (1 - 1/(1 + exp(-Be %*% X_val)))
  
  pbeta(t, a_hat, b_hat)    ## ROC
}

binorm_ROC <- function(coefs, t, X_val = matrix(c(1, 45, 5), nrow = 3)){
  ga_1 <- coefs[1]
  ga_2 <- coefs[2]
  Be <- coefs[c(3, 4, 5)] %>% matrix %>% t
  
  pnorm(ga_1 + ga_2 * qnorm(t) + c(Be %*% X_val))
}

# plot of ROC curves
ggplot(data.frame(t = c(0, 1)), aes(t)) +
  stat_function(fun = binorm_ROC, args = list(coefs = coefs_PDF)) + 
  stat_function(fun = Beta_ROC, args = list(coefs = coefs_Be),
                color = "red") + 
  ylab("ROC(t)")
```